Hire Ed: Job Market Dynamics for Tenure-Track Faculty Positions in Archaeology

### 2025-05-01 analysis/paper/article.qmd
increase text size and improve number placement on Fig 2 map

ggsave(here("analysis",
            "figures", 
            "fig-map-and-carnegie-classification.png"),
       plot = p_map_c,
       bg ="white",
       h = 7, # experiment with h and w to get the right size and proportion
       w = 12,
       units = "in",
       dpi = 900) # make the image nice and crisp))

@@

# show figure from PNG file
knitr::include_graphics(here("analysis",
            "figures",
            "fig-map-and-carnegie-classification.png"))
```

>>>>

# save this as SVG, then edit by hand to position the numbers on the
# map nicely, then export that hand-edited SVG as a png to show in the
# paper 
ggsave(here("analysis",
            "figures", 
            "fig-map-and-carnegie-classification.svg"),
       plot = p_map_c,
       bg ="white",
       h = 7, # experiment with h and w to get the right size and proportion
       w = 12,
       units = "in",
       dpi = 900) # make the image nice and crisp))

@@

# show figure from PNG file, this is after hand edits to place the
# numbers on the map nicely
knitr::include_graphics(here("analysis",
            "figures",
            "fig-map-and-carnegie-classification-hand-edit.png"))
```
